An Elaboration on\\Order-Adaptive Regularisation for Variational Optical Flow:\\Global, Local and in Between

### 2018-07-27 seminar_vof/paper/paper.tex
more schemes

\newcommand{\lam}{\lambda}
\newcommand{\trans}{\quad\bigg|\;}
\newcommand{\Trans}{\quad\Bigg|\;}
% matrix shortcut
\newcommand{\mat}[1]{\begin{pmatrix} #1 \end{pmatrix}}
% matrix shortcut with increased vertical spacing
\newcommand{\Mat}[1]{\begingroup
\renewcommand*{\arraystretch}{1.5}
\mat{#1}
\endgroup}
% matrix format but without braces (secretly a matrix)
\newcommand{\secretMat}[2][r]{\begin{matrix*}[#1] #2 \end{matrix*}}
% matrix format but without braces (secretly a matrix) with increased vertical spacing
\newcommand{\SecretMat}[2][r]{\begingroup
\renewcommand*{\arraystretch}{1.7}
\secretMat[#1]{#2}
\endgroup}
% shortcuts for df/dx stuff in derivative
\newcommand{\der}{\partial}
\newcommand{\deriv}[2]{\frac{\der #1}{\der #2}}
% make star '*' become \cdot (normal multiplication sign)
\mathcode`\*="8000
{\catcode`\*\active\gdef*{\cdot}}
\newcommand{\Real}{\mathbb{R}}
\newcommand{\flow}{\vec{u}}
\newcommand{\x}{\vec{x}}
\newcommand{\y}{\vec{y}}
\newcommand{\ev}{\vec{r}}
\newcommand{\aaux}{\vec{a}}
\newcommand{\baux}{\vec{b}}
\newcommand{\T}{^\top}
\newcommand{\argmin}{\mathop{\mathrm{argmin}}}
\newcommand{\charbonnier}{\psi_{\text{Ch}}}
\newcommand{\peronamalik}{\psi_{\text{PM}}}
\newcommand{\Rfirst}{R_{1\text{st}}}
\newcommand{\Rsecond}{R_{2\text{nd}}}
\newcommand{\jacob}{\mathcal{J}}

@@

\subsection{Non-Local Scheme}
Since the local scheme allows for different regularization order per pixel based on a decision which only takes that pixels location into account, regularization order may fluctuate a lot in this model.

>>>>

\newcommand{\lam}{\lambda}
\newcommand{\trans}{\quad\bigg|\;}
\newcommand{\Trans}{\quad\Bigg|\;}
% matrix shortcut
\newcommand{\mat}[1]{\begin{pmatrix} #1 \end{pmatrix}}
% matrix shortcut with increased vertical spacing
\newcommand{\Mat}[1]{\begingroup
\renewcommand*{\arraystretch}{1.5}
\mat{#1}
\endgroup}
% matrix format but without braces (secretly a matrix)
\newcommand{\secretMat}[2][r]{\begin{matrix*}[#1] #2 \end{matrix*}}
% matrix format but without braces (secretly a matrix) with increased vertical spacing
\newcommand{\SecretMat}[2][r]{\begingroup
\renewcommand*{\arraystretch}{1.7}
\secretMat[#1]{#2}
\endgroup}
% shortcuts for df/dx stuff in derivative
\newcommand{\der}{\partial}
\newcommand{\deriv}[2]{\frac{\der #1}{\der #2}}
% make star '*' become \cdot (normal multiplication sign)
\mathcode`\*="8000
{\catcode`\*\active\gdef*{\cdot}}
\newcommand{\Real}{\mathbb{R}}
\newcommand{\flow}{\vec{u}}
\newcommand{\x}{\vec{x}}
\newcommand{\y}{\vec{y}}
\newcommand{\ev}{\vec{r}}
\newcommand{\aaux}{\vec{a}}
\newcommand{\baux}{\vec{b}}
\newcommand{\T}{^\top}
\newcommand{\argmin}{\mathop{\mathrm{argmin}}}
\newcommand{\charbonnier}{\psi_{\text{Ch}}}
\newcommand{\peronamalik}{\psi_{\text{PM}}}
\newcommand{\Rfirst}{R_{1\text{st}}}
\newcommand{\Rsecond}{R_{2\text{nd}}}
\newcommand{\jacob}{\mathcal{J}}
\newcommand{\patch}{\mathcal{N}}
\newcommand{\cnl}{c_{\text{nl}}}
\newcommand{\cNl}{\overset{\_}{c}_{\text{nl}}}

@@

\subsection{Non-Local Scheme}
Since the local scheme allows for different regularization order per pixel based on a decision which only takes that pixels location into account, regularization order may fluctuate a lot in this model.
To make the descision more consistent with the pixels neighorhood, the weighting function $c_{\text{local}}(\x)$ is altered to
take a rectangular shaped patch of pixels around it into account.
\begin{flalign}
\cNl(\x) = \frac{1}{|\patch(\x)|}\int_{\patch(\x)}\cnl(\y)\;d\y 
&&\\
R_\text{nl}(\flow,\cnl) = \int_\Omega \inf_{\aaux,\baux}\big[\; \cNl*S_1(\flow) 
& + (1-\cNl)*\big(S_2(\flow,\aaux,\baux) +T\big)
&&\\
& + \beta*S_\text{aux}(\aaux,\baux)
+ \lambda*\phi(\cnl)\;\big] \;d\x \nonumber&&
\end{flalign}
Here $\mathcal{N}(\x)$ denotes the patch of $\x$ and $|\mathcal{N}(\x)|$ the patch size which is used for normalization.
To find $\cnl$, $R_\text{nl}(\flow,\cnl)$ is minimized with respect to it.
\begin{flalign}
\frac{\partial R(\flow,\cnl)}{\partial \cnl} = \cdots
&&\\
\text{derivation of~} \cnl \dots
&&\\
\cnl = \cdots
&&
\end{flalign}

\subsection{Region-Based Scheme}
The non-local scheme takes a neighborhood around a pixel into account for the descision on regularization order.
To push it yet a little further, the region based scheme decides on order leveraging a level set function $z(\x):\Omega\to\mathbb{R}$ which devides the image space into first and second order regularized regions.
The corresponding regularizer reads as follows.
\begin{flalign}
&R(\flow,z) = \int_\Omega c_\text{rgn}(z)*S_1 + (1-c_\text{rgn}(z))*(S_2 + T) + \theta*|\nabla c_\text{rgn}(z)| \;d\x
&&\\
&c_\text{rgn}(z) = \frac{1}{1+e^{z/\lambda}}
&&
\end{flalign}
Here $c_\text{rgn}$ is as well a sigmoid function, but choosen to approximate the heaviside funtion ($\lambda\to 0$) in order to obtain hard boundaries for the regions defined by $z$.
The selection term from the previous schemes has been replaced by a smoothness term on $c_\text{rgn}$ which penalizes level set functions with lots of sign changes.
Due to this penalization short paths for $z(\x)=0$ are favored resulting in smooth region boundaries.
